Gas Fractions of Galaxies Across Simulations

### 2018-07-12 mnras_template.tex
Update on Overleaf.

\begin{figure*}
\includegraphics[width = 0.33\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
\includegraphics[width = 0.33\linewidth]{MHI_Mstar_binned_IQR.png}
\includegraphics[width = 0.33\linewidth]{gasless_fraction_mstar.png}
\caption{{\bf Left:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each. Unlike in Figure~\ref{fig:fgas mstar 2D}, this includes galaxies with zero neutral gas mass. {\bf Middle} The running median of gas mass as a function of stellar mass for each dataset with shading denoting the IQR. {\bf Right:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas. The percent of all galaxies without gas in each dataset is shown in the legend.}
\label{fig:linear fgas mstar}
\end{figure*}

@@

>>>>

\begin{figure*}
\includegraphics[width = 0.3\linewidth]{fgas_mstar_binned_IQR_logged.png}
\includegraphics[width = 0.3\linewidth]{MHI_Mstar_binned_IQR.png}
\includegraphics[width = 0.3\linewidth]{gasless_fraction_mstar.png}
\caption{{\bf Left:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each. Unlike in Figure~\ref{fig:fgas mstar 2D}, this includes galaxies with zero neutral gas mass. {\bf Middle} The running median of gas mass as a function of stellar mass for each dataset with shading denoting the IQR. {\bf Right:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas. The percent of all galaxies without gas in each dataset is shown in the legend.}
\label{fig:linear fgas mstar}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 0.49\linewidth]{MHI_Mstar_binned_IQR_bradford_fgas_cut}
\includegraphics[width=0.49\linewidth]{fgas_mstar_binned_IQR_logged_bradford_fgas_cut.png}
\caption{Running medians of simulated galaxies in comparison to isolated galaxies from Bradford et. al. 2015 and the xGASS survey. The same Bradford et. al. 2015 limiting gas fraction thresholds were applied to all plotted data.}
\label{fig:fgas DSFMS panel}
\end{figure*}
